Postural changes mediate children's visual access to social information

### 2018-01-16 writeup-cogsci-jan14/cogsci2018_faceOnly.Rmd
cleanup and get rid of VJ for plotting

```{r, message=FALSE, warning=FALSE, results='asis'}
### Needs to be consolidated so that we're aren't rereading all of these files here...
# data_vj<- read_csv("../data/final_output/viola.csv") %>%
#   distinct(video, frame, .keep_all = TRUE)
# 
# data_mtcnn <- read_csv("../data/final_output/mtcnn3.csv") %>%
#   distinct(video, frame, .keep_all = TRUE)
# 
# data_openpose <- read_csv("../data/final_output/openpose_results_truncated_2.csv")%>%
#   distinct(name, frame, .keep_all = TRUE) %>%
#   mutate(frame = sprintf("%05d", as.numeric(frame) + 1)) %>%
#   mutate(is_face = ifelse(Nose_conf != 0, "True", "False")) %>%
#   select(group, name, frame, is_face) %>%
#   rename(video = name)

d <- read_csv("../data/consolidateddata/consolidated_data_4dets.csv") %>%
  mutate(posture = factor(posture), orientation = factor(orientation))

@@

## couple of helper functions

evaluate <- function(a, b) {
  if (a == TRUE) {
    if (a == b) return ("TP") # was face, said face
    else return("FN") # was face, missed face
  }
  else {
    if (a == b) return("TN") # was not face, said not face
    else return("FP") # was not face, said face
  }
}

@@

performance <- ground_truth_data  %>%
  mutate(frame=as.numeric(frame), subid=video) %>%
  left_join(dlong)   %>%
  mutate(detector_is_face = detection, is_face = as.logical(is_face)) %>%
  rowwise() %>%
  mutate(result = evaluate(is_face, detector_is_face)) %>%
  group_by(detectorType,sample_type) %>%
  summarise(tp=sum(result == "TP"), fp=sum(result == "FP"), fn=sum(result=="FN")) %>%
  group_by(detectorType,sample_type) %>%
  summarise(p = tp / (tp + fp), r = tp / (tp + fn), f=( 2 * p * r )/ (p + r))
```

```{r xtable, results="asis"}
 tab2 <- xtable::xtable(performance, digits=3, caption = "Detector performance")
```

<!-- \begin{table}[H] -->
<!-- \centering -->
<!-- \begin{tabular}{rrrr} -->
<!--   \hline -->
<!--   & P & R & F \\  -->
<!-- \hline -->
<!-- OpenPose High Density Sample & 0.99 & 0.87 & 0.93 \\  -->
<!-- OpenPose Random Sample & 0.71 & 0.92 & 0.80 \\ -->
<!-- MTCNN High Density Sample & 0.84 & 1.00 & 0.91 \\  -->
<!-- MTCNN Random Sample & 0.95 & 0.75 & 0.84 \\  -->
<!--    \hline -->
<!-- \end{tabular} -->
<!-- \caption{Face detector performance}  -->
<!-- \end{table} -->

@@

```{r echo=FALSE, include=FALSE}
d <- read_csv("../data/consolidateddata/consolidated_data_4dets.csv") %>%
  mutate(posture = factor(posture), orientation = factor(orientation))

## make long form version for plotting both face detections on same graph
dlong <- d %>%
  mutate(id = paste(subid,frame)) %>%
  gather(key = detectorType, value = detection, faceMT, faceOP) %>%
  mutate(detectorType=as.factor(detectorType))

>>>>

```{r, message=FALSE, warning=FALSE, results='asis'}
d <- read_csv("../data/consolidateddata/consolidated_data_4dets.csv") %>%
  mutate(posture = factor(posture), orientation = factor(orientation))

@@

## couple of helper functions
evaluate <- function(a, b) {
  if (a == TRUE) {
    if (a == b) return ("TP") # was face, said face
    else return("FN") # was face, missed face
  }
  else {
    if (a == b) return("TN") # was not face, said not face
    else return("FP") # was not face, said face
  }
}

@@

## evaluate detectors
performance <- ground_truth_data  %>%
  mutate(frame=as.numeric(frame), subid=video) %>%
  left_join(dlong)   %>%
  mutate(detector_is_face = detection, is_face = as.logical(is_face)) %>%
  rowwise() %>%
  mutate(result = evaluate(is_face, detector_is_face)) %>%
  group_by(detectorType,sample_type) %>%
  summarise(tp=sum(result == "TP"), fp=sum(result == "FP"), fn=sum(result=="FN")) %>%
  group_by(detectorType,sample_type) %>%
  summarise(p = tp / (tp + fp), r = tp / (tp + fn), f=( 2 * p * r )/ (p + r))
```

```{r xtable, results="asis"}
 tab2 <- xtable::xtable(performance, digits=3, caption = "Detector performance", type="latex", comment = F, table.placement = "H")
```

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
  \hline
 & detectorType & sample\_type & p & r & f \\ 
  \hline
1 & MTCNN & high\_density & 0.841 & 1.000 & 0.914 \\ 
  2 & MTCNN & random & 0.947 & 0.750 & 0.837 \\ 
  3 & OpenPose & high\_density & 0.995 & 0.863 & 0.924 \\ 
  4 & OpenPose & random & 0.710 & 0.917 & 0.800 \\ 
  5 & ViolaJones & high\_density & 0.991 & 0.495 & 0.660 \\ 
  6 & ViolaJones & random & 0.389 & 0.292 & 0.333 \\ 
   \hline
\end{tabular}
\caption{Detector performance} 
\end{table}

@@

```{r echo=FALSE, include=FALSE}
# get rid of violajones
dlong <- dlong %>%
  filter(detectorType!="faceVJ")
